---
title: "Forecastmodel"
author: "M. Klein"
date: "29-1-2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("plyr")
library("dplyr")
library("ggplot2")
library(plotly)
library("caret")
library(RWeka)
library("formattable")
library("parallel")
library("doParallel")

source("patrolData.R")
source("util.R")
source("model.R")
source("buienradar.R")
```

##Loading the data
```{r load, cache=TRUE}
holiday <- loadHoliday()
holidays <- loadHolidays()
weatherHourly <- loadWeatherHourly()
trackDetail <- loadTrackDetail()
trackSector <- loadTrackSector()
sectorHourCounts <- loadSectorHourCounts()
```

#Features
```{r features, cache=TRUE, dependson='load'}
source("model.R")

data <- createModelData(trackDetail, trackSector, sectorHourCounts, holiday, holidays, weatherHourly)
```

#Model

The final modal is created on the whole data set with cross validation.    
```{r train, cache=TRUE, warning=FALSE}
set.seed(2017-01-29)
 
 cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
 registerDoParallel(cluster)
     
# fitControl <- trainControl(method = "cv",
#                            number = 10,
#                            allowParallel = TRUE)
#     
dataTrack <- data %>% filter(id==6,hour>=6 & hour <=21) %>% select(-id, -timestamp)
intrain <- createDataPartition(y=dataTrack$count, p=1, list=FALSE) #0.7
predictors <- dataTrack[intrain,] #%>% select(-count)
#predictorsCount <- dataTrack[intrain,"count"]
# validation <- dataTrack[-intrain,"count"]
# validationClasse <- dataTrack[-intrain,] %>% select(-count)
 
 ptm <- proc.time()
# md <- train(predictors,predictorsCount, method="rf", trControl = fitControl, nodesize = 5, ntree = 200)
 md <- M5P(count~., data=predictors, control = Weka_control(R = FALSE))
 md2 <- M5P(count~., data=predictors, control = Weka_control(R = TRUE))
 md3 <- M5P(count~., data=predictors, control = Weka_control(R = FALSE, N = TRUE))
 md4 <- M5P(count~., data=predictors, control = Weka_control(R = FALSE, U = TRUE))
 print(proc.time() - ptm)
 format(object.size(md),units="Kb")
 #print(md)
 summary(md)
 summary(md2)
 evaluate_Weka_classifier(md, predictors, numFolds = 10)
 evaluate_Weka_classifier(md2, predictors, numFolds = 10)
```

```{r fc, cache=TRUE}
#weatherForecast <- getWeatherForecast()

forecastData <- createForecastData(2, ymd("2017-01-30"), 14, holiday, holidays, weatherForecast)
predictors <- forecastData %>% select(-timestamp)

forecastData$count <- predict(md, predictors)
forecastData$count2 <- predict(md2, predictors)
forecastData$count3 <- predict(md3, predictors)
forecastData$count4 <- predict(md4, predictors)

plot_ly(data=forecastData,  x = ~timestamp, 
              y = ~count, mode = "lines", type="scatter", name="R = FALSE") %>%
        add_trace(y = ~count2, name = "R = TRUE", mode = 'lines') %>%
        add_trace(y = ~count3, name = "R = FALSE -N", mode = 'lines') %>%
        add_trace(y = ~count4, name = "R = FALSE -U", mode = 'lines') %>%
                layout(                yaxis = list(rangemode = "tozero")) 


```
The final modal uses mtry = `r as.numeric(md$bestTune)` with an accurancy of `r percent(md$results[md$results$mtry==as.numeric(md$bestTune),2])`. This is better than the minimal threshold of 99%. The in of sample error is `r percent(1-md$results[md$results$mtry==as.numeric(md$bestTune),2])`

#Final Model
```{r finalModel, cache=TRUE,  warning=FALSE}

trackModelsFinal <- trackDetail %>% filter(trackType==0) %>% select(id,name)
dataFinal <- createModelData(trackDetail, trackSector, sectorHourCounts, holiday, holidays, weatherHourly)

mds <- list()
for (trackId in trackModelsFinal$id) {
    print(trackModelsFinal[trackModelsFinal$id==trackId,]$name)
    mdt <- createModelRf(dataFinal, trackId)
    print(mdt)
    mds[[trackModelsFinal[trackModelsFinal$id==trackId,]$name]] <- mdt
}

```
```{r finalModel2, cache=TRUE,  warning=FALSE}

trackModelsFinal2 <- trackDetail %>% filter(trackType==0) %>% select(id,name)
dataFinal2 <- createModelData(trackDetail, trackSector, sectorHourCounts, holiday, holidays, weatherHourly)

mds2 <- list()
for (trackId in trackModelsFinal2$id) {
    print(trackModelsFinal2[trackModelsFinal2$id==trackId,]$name)
    mdt2 <- createModel(dataFinal2, trackId, method = "M5P", regression = TRUE)
#    print(mdt2)
    mds2[[trackModelsFinal2[trackModelsFinal2$id==trackId,]$name]] <- mdt2
}
format(object.size(mds2), units = "Kb")
```

```{r forecast, cache=TRUE}
weatherForecast <- getWeatherForecast()

forecastDataFinal <- createForecastData(1, ymd("2017-01-30"), 14, holiday, holidays, weatherForecast)

round <- TRUE
forecastDataFinal$countAM <- forecastTrack(mds2[["Amerongen"]], forecastDataFinal, round = round)
forecastDataFinal$countHG <- forecast(mds2[["Hoge Ginkel"]], forecastDataFinal, round = round)
forecastDataFinal$countKW <- forecast(mds2[["Kwintelooijen"]], forecastDataFinal, round = round)
forecastDataFinal$countLE <- forecast(mds2[["Leersum"]], forecastDataFinal, round = round)
forecastDataFinal$countRH <- forecast(mds2[["Rhenen"]], forecastDataFinal, round = round)
forecastDataFinal$countZE <- forecast(mds2[["Zeist"]], forecastDataFinal, round = round)
forecastDataFinal$countAU <- forecast(mds2[["Austerlitz"]], forecastDataFinal, round = round)

plot_ly(data=forecastDataFinal,  x = ~timestamp, 
              y = ~countAM, name = 'Amerongen', mode = "lines", type="scatter") %>%
    add_trace(y = ~countHG, name = 'Hoge Ginkel', mode = 'lines') %>%
    add_trace(y = ~countKW, name = 'Kwintelooijen', mode = 'lines') %>%
    add_trace(y = ~countLE, name = 'Leersum', mode = 'lines') %>%
    add_trace(y = ~countRH, name = 'Rhenen', mode = 'lines') %>%
    add_trace(y = ~countZE, name = 'Zeist', mode = 'lines') %>%
    add_trace(y = ~countAU, name = 'Austerlitz', mode = 'lines') %>%
                layout(yaxis = list(rangemode = "tozero")) 
    
```

