---
title: "Forecastmodel"
author: "M. Klein"
date: "29-1-2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("plyr")
library("dplyr")
library("ggplot2")
library(plotly)
library("caret")
library("randomForest")
library("formattable")
library("parallel")
library("doParallel")

source("patrolData.R")
source("util.R")
source("model.R")
source("buienradar.R")
```

##Loading the data
```{r load, cache=TRUE}
holiday <- loadHoliday()
holidays <- loadHolidays()
weatherHourly <- loadWeatherHourly()
trackDetail <- loadTrackDetail()
trackSector <- loadTrackSector()
sectorHourCounts <- loadSectorHourCounts()
```

#Features
```{r features, cache=TRUE, dependson='load'}
source("model.R")

data <- createModelData(trackDetail, trackSector, sectorHourCounts, holiday, holidays, weatherHourly)
```

#Model

The final modal is created on the whole data set with cross validation.    
```{r train, cache=TRUE, warning=FALSE}
set.seed(2017-01-29)

cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)
    
fitControl <- trainControl(method = "cv",
                           number = 10,
                           allowParallel = TRUE)
    
dataTrack <- data %>% filter(id==2,hour>=6 & hour <=21) %>% select(-id, -timestamp)
intrain <- createDataPartition(y=dataTrack$count, p=0.7, list=FALSE) #0.7
predictors <- dataTrack[intrain,] %>% select(-count)
predictorsCount <- dataTrack[intrain,"count"]
validation <- dataTrack[-intrain,"count"]
validationClasse <- dataTrack[-intrain,] %>% select(-count)

ptm <- proc.time()
md <- train(predictors,predictorsCount, method="rf", trControl = fitControl, nodesize = 5, ntree = 200)
print(proc.time() - ptm)

print(md)
```

```{r fc, cache=TRUE}
weatherForecast <- getWeatherForecast()

forecastData <- createForecastData(2, ymd("2017-01-30"), 14, holiday, holidays, weatherForecast)
predictors <- forecastData %>% select(-timestamp)

forecastData$count <- predict(md, predictors)

plot_ly(data=forecastData,  x = ~timestamp, 
              y = ~count, name = 'fc', mode = "lines", type="scatter") %>%
                layout(                yaxis = list(rangemode = "tozero")) 


```
The final modal uses mtry = `r as.numeric(md$bestTune)` with an accurancy of `r percent(md$results[md$results$mtry==as.numeric(md$bestTune),2])`. This is better than the minimal threshold of 99%. The in of sample error is `r percent(1-md$results[md$results$mtry==as.numeric(md$bestTune),2])`

#Final Model
```{r finalModel, cache=TRUE,  warning=FALSE}

trackModelsFinal <- trackDetail %>% filter(trackType==0) %>% select(id,name)
dataFinal <- createModelData(trackDetail, trackSector, sectorHourCounts, holiday, holidays, weatherHourly)

mds <- list()
for (trackId in trackModelsFinal$id) {
    print(trackModelsFinal[trackModelsFinal$id==trackId,]$name)
    mdt <- createModelRf(dataFinal, trackId)
    print(mdt)
    mds[[trackModelsFinal[trackModelsFinal$id==trackId,]$name]] <- mdt
}

```
```{r finalModel2, cache=TRUE,  warning=FALSE}

trackModelsFinal2 <- trackDetail %>% filter(trackType==0) %>% select(id,name)
dataFinal2 <- createModelData(trackDetail, trackSector, sectorHourCounts, holiday, holidays, weatherHourly)

mds2 <- list()
for (trackId in trackModelsFinal2$id) {
    print(trackModelsFinal2[trackModelsFinal2$id==trackId,]$name)
    mdt2 <- createModelRf2(dataFinal2, trackId)
    print(mdt2)
    mds2[[trackModelsFinal2[trackModelsFinal2$id==trackId,]$name]] <- mdt2
}

```


```{r cache=TRUE}
mdf2 <- mds2[["Amerongen"]]

dataTrack <- data %>% filter(id==2,hour>=6 & hour <=21) %>% select(-id)
intrain <- createDataPartition(y=dataTrack$count, p=0.01, list=FALSE) #0.7
predictors <- dataTrack[intrain,] %>% select(-count)


fc <- predict(mdf2, predictors)
vg <-data.frame(r=dataTrack[intrain,]$count, fc =fc, fci = as.integer(fc))
```

```{r forecast, cache=TRUE}
weatherForecast <- getWeatherForecast()

forecastDataFinal <- createForecastData(1, ymd("2017-01-30"), 14, holiday, holidays, weatherForecast)

forecastDataFinal$countAM <- forecastRf(mds2[["Amerongen"]], forecastDataFinal)
forecastDataFinal$countHG <- forecastRf(mds2[["Hoge Ginkel"]], forecastDataFinal)
forecastDataFinal$countKW <- forecastRf(mds2[["Kwintelooijen"]], forecastDataFinal)
forecastDataFinal$countLE <- forecastRf(mds2[["Leersum"]], forecastDataFinal)
forecastDataFinal$countRH <- forecastRf(mds2[["Rhenen"]], forecastDataFinal)
forecastDataFinal$countZE <- forecastRf(mds2[["Zeist"]], forecastDataFinal)
forecastDataFinal$countAU <- forecastRf(mds2[["Austerlitz"]], forecastDataFinal)

plot_ly(data=forecastDataFinal,  x = ~timestamp, 
              y = ~countAM, name = 'Amerongen', mode = "lines", type="scatter") %>%
    add_trace(y = ~countHG, name = 'Hoge Ginkel', mode = 'lines') %>%
    add_trace(y = ~countKW, name = 'Kwintelooijen', mode = 'lines') %>%
    add_trace(y = ~countLE, name = 'Leersum', mode = 'lines') %>%
    add_trace(y = ~countRH, name = 'Rhenen', mode = 'lines') %>%
    add_trace(y = ~countZE, name = 'Zeist', mode = 'lines') %>%
    add_trace(y = ~countAU, name = 'Austerlitz', mode = 'lines') %>%
                layout(yaxis = list(rangemode = "tozero")) 
    
```


```{r trim, cache=TRUE}
format(object.size(mds2[["Amerongen"]]),units="Kb")
count <- predict(mds2[["Amerongen"]], forecastDataFinal)
trimmedModel <- mds2[["Amerongen"]]

trimmedModel$y <- NULL
trimmedModel$mse <- NULL
    trimmedModel$weights <- NULL
    trimmedModel$fitted.values <- NULL
    trimmedModel$model <- NULL
    trimmedModel$prior.weights <- NULL
    trimmedModel$residuals <- NULL
    trimmedModel$effects <- NULL
    trimmedModel$where <- NULL
trimmedModel$predicted <- NULL

names(trimmedModel$forest)
sapply(names(trimmedModel), function(x) { format(object.size(trimmedModel[x]),units="Kb") })
sapply(names(trimmedModel$forest), function(x) { format(object.size(trimmedModel$forest[x]),units="Kb") })


format(object.size(trimmedModel),units="Kb")
countTrimmed <- predict(trimmedModel, forecastDataFinal)
identical(count,countTrimmed)  

```
```{r}

```
